### 2022-08-29 chapters/optimization/python-dir/python_interperters.tex
add : python bitops

The reason of separation between data collection and energy calculation is to minimise any interference with the test so our sensor is a light c program running inside a docker container.
\subsection{tests preparation}

@@

\section{Results and finding}

\subsection{Preliminary stduies}
This part will be dedicated to analyse the initial behaviour of different python interpereters.
First we started with a typical benchmark binarrytree. where we compare the energy consumption of the different implementations.

\subsection{python and binarry operations }
The goal of this study is to look at how different Python implementations work while treating different binary operations .

@@

Table~ provides a detailed report on the energy consumption of different implementations of the code.

Except for \emph{Cython}, each implementation treats the binary operation the same. As one can see, Table~\ref{table:bitops} shows no difference in the energy consumption of those operations.

@@

The first, which is the interpreted one, uses approximately 500 joules per operation. The second is a non-optimized compilation that includes Cython and Nuitka and uses 10 times less energy than the first. And the final one, which has been fully optimized, uses 50 percent less energy. This category includes jit libraries, also known as numba, Python implementations that include JIT, also known as pypy, and shedskin, which transpile the source code into C and then use a C/C++ compiler to generate the binary, as opposed to cython and nuitka, which directly compile the python code.

To conclude this. JIT has a huge impact when it comes to binary functions, and the wrong choice of the implementation can lead to up to a 100x increase in energy consumption.

\section{placeholder}
introdution to the stufy
we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\% therefore the distrubution is not normal

for arrays and vectors  graalpython took so much time that we decided to remove it

@@

so the plan is to prove that there is a statistical difference
then we use the multiparameter optimization , howerver we stop in the phase where we calculate the score
because we dont know the weight of each parameter ( of tommti microbenchmark) and instead of doing the sum with the coefissients we use the radar plot to let the reader decide which one is the most suitable for his usage. howerver since the differences are gigantics we change the scale to logarithmic to be easier for the eye to read

@@

\input{table-envs.tex}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/dendogram_interpreters}
    \caption{Dendogram of the different implementations}
    \label{fig:dendogram}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/alltomti_performance}
    \caption{different interpererts optimisation }
    \label{fig:tommi_all}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__pypy2_pypy3}
    \caption{green factor of pypy }
    \label{fig:pypy2vspypy3}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython3_numba3_pypy3}
    \caption{comparaison of pypy vs python vs numba }
    \label{fig:p3}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython2_pypy2_numba2}
    \caption{comparaison of pypy vs python vs numba }
    \label{fig:p2}
\end{figure}

>>>>

The reason of separation between data collection and energy calculation is to minimise any interference with the test so our sensor is a light c program running inside a docker container.

\subsection{tests preparation}
\paragraph{workload}
To test our implementations, we employed the Tommti microbenchmarks suite~\footnote{\url{http://www.tommti-systems.de/main-Dateien/reviews/languages/benchmarks.html}}. A set of 13 microbenchmarks that examine common language features such as arithmetic operations, data structures and input/output manipulations, among others. In addition to these tests ,we implemented some binary operations to examine the behavior of the previous implementations when it comes to low-level operations that works only with registries.

@@

\section{Results and finding}
This section will be dedicated to the results of the experiments and the finding of the best implementation.
\paragraph{python and binarry operations }
The goal of this study is to look at how different Python implementations work while treating different binary operations .

@@

Table~~\ref{table:bitops} provides a detailed report on the energy consumption of different implementations of the code.
Besides \emph{Cython}, each implementation treats the binary operation the same. As one can see, Table~\ref{table:bitops} shows no difference in the energy consumption of those operations.

@@

The first, which is the interpreted one, uses approximately 500 joules per operation. The second is a non-optimized compilation that includes Cython and Nuitka and uses 10 times less energy than the first. And the final one, which has been fully optimized, uses 50 percent less energy. This category includes jit libraries, also known as numba, Python implementations that include JIT, also known as pypy, and shedskin, which transpile the source code into C and then use a C/C++ compiler to generate the binary, as opposed to cython and nuitka, which directly compile the python code.
To conclude this. JIT has a huge impact when it comes to binary operations, and the wrong choice of the implementation can lead to up to a 100x increase in energy consumption. In the other hand,Different binary operations exhibit the same behaviour when it comes to the energy consumption for all the implementations except Cython.

\section{introduction to the study}
Since we are in a comparative study, we first performed a shapiro normality test on the results, and almost all the p-values are  smaller than alpha=0.01\% therefore the distrubution is not normal. To make a comparaison we used Manwithyu's tests.
Table \ref{table:manwithyu} .

\input{table-envs-based-cpython.tex}
for arrays and vectors  graalpython took so much time that we decided to remove it

@@

then we use the multiparameter optimization , howerver we stop in the phase where we calculate the score
because we dont know the weight of each parameter ( of tommti microbenchmark) and instead of doing the sum with the coefissients we use the radar plot to let the reader decide which one is the most suitable for his usage. howerver since the differences are gigantics we change the scale to logarithmic to be easier for the eye to read

@@

\input{table-envs.tex}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/dendogram_interpreters}
    \caption{Dendogram of the different implementations}
    \label{fig:dendogram}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/alltomti_performance}
    \caption{different interpererts optimisation }
    \label{fig:tommi_all}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{imgs/tommti_compare__pypy2_pypy3}
%     \caption{green factor of pypy }
%     \label{fig:pypy2vspypy3}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython3_numba3_pypy3}
%     \caption{comparaison of pypy vs python vs numba }
%     \label{fig:p3}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython2_pypy2_numba2}
%     \caption{comparaison of pypy vs python vs numba }
%     \label{fig:p2}
% \end{figure}
